---
title: "Stats 20, W25 -- Homework 3"
author: "Sandra Pan -- 606155139"
date: "`r format(Sys.Date(), '%D')`"
output:
  pdf_document:
    toc: true
    toc_depth: '4'
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: show
---


## Question 1

### (a)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1a}
# Homework scores
scores <- c(87, 94, 68, 73,
91, 55, 82, 77,
90, 66)
# Student names (same length as scores)
students <- c("Alice", "Bob", "Charlie", "Diana",
"Alice", "Bob", "Charlie", "Diana",
"Alice", "Bob")
# Homework assignments (same length as scores)
assignments <- c("HW1", "HW1", "HW1", "HW1",
"HW2", "HW2", "HW2", "HW2",
"HW3", "HW3")

# extract the numeric vector of positions (indices) which the logical values are TRUE
bob_index <- which(students == "Bob")
bob_scores <- scores[bob_index]
bob_scores
```

### (b)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1b}
mean(bob_scores)
```

### (c)
<!-- USE THE CODE CHUNKS BELOW -->
```{r Question 1c first}
hw2_index <- which(assignments == "HW2")
hw2_scores <- scores[hw2_index]
hw2_scores

```

```{r Question 1c second}
hw2_students <- students[hw2_index]
hw2_students
```

### (d)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1d}
low_scores_index <- which(scores < 70)
low_scores_index
unique(students[low_scores_index])
```

### (e)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1e}
scores[scores < 70] <- 0
# rewrite bob_scores to include the 0
bob_scores <- scores[bob_index]
mean(bob_scores)
```


## Question 2

### (a)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 2a}
commute_times <- c(14, 12, 20, 19, 15, 20, 28, 20, 20, 18)
# which days did andy have a commute time that was more than one sd away from the mean commute time?
standard_dev <- sd(commute_times)
mean_time <- mean(commute_times)
times <- commute_times[commute_times < abs(mean_time - standard_dev)]
times
```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL) -->
I created a vector called commute_times. I then created objects that were the the standard deviation and mean of commute_times. Then, I created another object called times that computed whether the values in commute times were outside of one standard deviation of the mean.

### (b)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 2b}
within_times <- commute_times[commute_times > abs(mean_time - standard_dev)]
within_times
```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL) -->
I used the same code as part a, but I changed `commute_times[commute_times < abs(mean_time - standard_dev)]` to `commute_times[commute_times > abs(mean_time - standard_dev)]`. The changing of less than to greater than sign gave me the commute times that were within one SD of the mean. 

### (c)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 2c}
length(within_times) / length(commute_times)
```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL) -->
To compute the proportion of days that Andy had a commute time that was within one sd of the mean commute time, I took my answer from part b that computed the times that were within one sd (also known as within_times). Then, I divided the `length(within_times) / length(commute_times)` to compute the proportion of times that were within one sd compared to the length of all the times.  

## Question 3

```{r Question 3}
NA & TRUE
NA & FALSE
NA | TRUE
NA | FALSE
```
<!-- ENTER YOUR EXPLANATION BELOW, FEEL FREE TO EDIT THE ABOVE CODE CHUNK -->
In the first line, `NA & TRUE` will output `NA` because NA in a logical vector represents a missing logical value, so it could either be TRUE or FALSE. In the second line,`NA & FALSE`, it will return FALSE because if NA can be TRUE or FALSE, then the & operator will output FALSE because of the FALSE value. In the third line, `NA | TRUE`, the output will be TRUE because if it is or, NA could be true or false and the output would still be true regardless. In the final line. `NA | FALSE`, the output would be NA, because NA can be true or false, and it wouldn't directly output FALSE.

## Question 4

<!-- PUT YOUR CODE FROM HW 1 HERE -->
The code I wrote for HW 1 is shown above, and it is vectorized because it goes through each element across the entire vector.

```{r Question 4 background} 
cents <- 47
quarters <- cents %/% 25
cents_now <- cents - quarters*25

dimes <- cents_now %/% 10
cents_now <- cents_now - dimes*10

nickels <- cents_now %/% 5
cents_now <- cents_now - nickels*5

pennies <- cents_now %/% 1
cents_now <- cents_now - pennies*1

min_coins <- quarters + dimes + nickels + pennies
min_coins
```

### (a)
<!-- ENTER YOUR ANSWER BELOW -->
<!-- USE THE CODE CHUNK BELOW IF YOU'D LIKE -->
```{r Question 4a}
cents <- 1:100 

quarters <- cents %/% 25
cents_now <- cents - quarters*25

dimes <- cents_now %/% 10
cents_now <- cents_now - dimes*10

nickels <- cents_now %/% 5
cents_now <- cents_now - nickels*5

pennies <- cents_now %/% 1
cents_now <- cents_now - pennies*1

min_coins <- quarters + dimes + nickels + pennies
min_coins
# is it vectorized? check the length 
length(min_coins) == length(cents)
```

### (b)
<!-- ENTER YOUR ANSWER BELOW, IT CAN BE JUST COMMANDs; NO NEED TO STORE OBJECTs -->
```{r Question 4b}
cents <- 1:99

quarters <- cents %/% 20
cents_now <- cents - quarters*25

dimes <- cents_now %/% 10
cents_now <- cents_now - dimes*10

nickels <- cents_now %/% 5
cents_now <- cents_now - nickels*5

pennies <- cents_now %/% 1
cents_now <- cents_now - pennies*1

min_coins <- quarters + dimes + nickels + pennies
min_coins

# find where the indices = max number of coins
max(min_coins)
# which coins does min_coins >= 9?
which(min_coins >= 9)

```


## Question 5

### (a)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 5a}
x <- c(FALSE, FALSE, TRUE, TRUE, FALSE) #[1] FALSE
my_table <- table(x) # gives the counts in the table
# find the name where my_table is true 
names(my_table[my_table == max(my_table)])

x <- c(1, 2, 3, 1, 2) # [1] 1 2
my_table <- table(x)
names(my_table[my_table == max(my_table)])

x <- c(3, 3, 2, 2, 1) # [1] 2 3 or [1] 3 2 is fine
my_table <- table(x)
names(my_table[my_table == max(my_table)])



```

### (b)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 5b}
x <- c(FALSE, FALSE, TRUE, TRUE, FALSE) # [1] FALSE
my_table <- unique(table(x))
all_modes <- names(my_table[my_table == max(my_table)])
unique(x)[unique(x) %in% all_modes][1]

x <- c(1, 2, 3, 1, 2) # [1] 1
my_table <- table(x)
all_modes <- names(my_table[my_table == max(my_table)])
unique(x)[unique(x) %in% all_modes][1]

x <- c(3, 3, 2, 2, 1) # [1] 3
my_table <- table(x)
all_modes <- names(my_table[my_table == max(my_table)])
unique(x)[unique(x) %in% all_modes][1]


```



## Question 6

<!-- MODIFY THE CODE CHUNK BELOW -->
```{r Question 6a}
jerry <- (2:8 * (5 %% 3^(-2:7))) > 2
jerry

```






